Computing Entropies With Nested Sampling

### 2017-07-12 paper/ms.tex
Removed leading space
Removed unneeded reference

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{
Department of Statistics, The University of Auckland, Private Bag 92019,
Auckland 1142, New Zealand}

@@

In physics and astronomy, it is common to measure an oscillating signal
at a set of times $\{t_1, ..., t_n\}$, in order to infer the amplitude,
period, and phase of the signal \citep{bretthorst}.
Here, I demonstrate the algorithm on a toy version
of Bayesian experimental design: at what times should the signal be
observed in order to obtain as much information as possible about the
period? To answer this, we need to be able to calculate the mutual
information between the unknown period and the data.

>>>>

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{Department of Statistics, The University of Auckland, Private Bag 92019,
Auckland 1142, New Zealand}

@@

In physics and astronomy, it is common to measure an oscillating signal
at a set of times $\{t_1, ..., t_n\}$, in order to infer the amplitude,
period, and phase of the signal.
Here, I demonstrate the algorithm on a toy version
of Bayesian experimental design: at what times should the signal be
observed in order to obtain as much information as possible about the
period? To answer this, we need to be able to calculate the mutual
information between the unknown period and the data.
